Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-02 robdml.tex
tex

Our core contribution is the improvement in adversarial training efficiency
through HM.
%
Since regular training and the min-max adversarial training can be expressed
as two boundary cases as HM, Graduate Adversary is modeled as an ``intermediate
hardness'' the two cases.
%
Enforcing the previously neglected Intra-Class Structure is also beneficial
for model robustness and adversarial training efficiency.

Adversarial robustness is important for DML applications, but
the existing defenses still suffer from low efficiency and low
performance.
%
In this paper, 
Hardness Manipulation is proposed as as a flexible tool to create
adversarial examples for more efficient adversarial training.
%
Meanwhile, Gradual Adversary is proposed as a family of pseudo-hardness
functions to better balance the training objectives.
%
Besides, an Intra-Class Structure penalty is proposed to enforce better
embedding structure for higher robustness.
%
According to experimental evaluations, the proposed method overwhelmingly
outperforms the state-of-the-art defenses.

>>>>

Adversarial robustness is important for DML applications.
%
Our core contribution is the improvement in adversarial training efficiency
through HM.
%
Since regular training and the min-max adversarial training can be expressed as
two boundary cases as HM, Graduate Adversary is modeled as an ``intermediate
hardness'' the two cases, and is effective.
%
Enforcing the previously neglected Intra-Class Structure can further improve 
model robustness and adversarial training efficiency.
%
Our method outperforms previous methods.
